Introducing Statistical Design of Experiments to SPARQL Endpoint Evaluation

### 2013-10-11 exp1/present2013.tex
Lenths method
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@662 43ef1190-90fd-4dd7-a769-d0121f02b80e
Martin's comments
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@663 43ef1190-90fd-4dd7-a769-d0121f02b80e

\begin{frame}{Objective}

To introduce a path to critical practice of evaluations, that makes
use of contemporary statistical techniques, to establish a practice
that can be used to refute assertions on performance.

The focus is didactical, and the experiment we present is a toy
example.

@@

\end{frame}
% TODO explain Lenth
\note{Don't worry about the axes}
\note{Yes, the Implementation is better, we knew that, joins are
  naturally strong}
\note{``Union'', ``Optional'' and ``Lang'' demanding things}
\note{``BGPComp:Lang'' and ``Lang:Union'' interactions might be due to
  that many more triples need to be searched for a language tag in one
  of the levels of the interacting factors.}
\note{But what about ``Implement::TripleC''?}
\note{We want to do a hypothesis test}
\note{Two factors do not contribute significantly to the variation
  ``Range'' and ``Machine''}

>>>>

\begin{frame}{Objective}
  \begin{itemize}
  \item To introduce a path to critical practice of evaluations, that makes
use of contemporary statistical techniques, to establish a practice
that can be used to refute assertions on performance.
\item The focus is didactical, and the experiment we present is a toy
example.
\item To apply a well established method in statistics, rarely used in
  Computer Science, to SPARQL endpoint evaluation.

@@

\end{frame}
\note{Unreplicated, so we don't have a standard error, so Lenth used
  a restricted subset the median of the effects to create a Pseudo
  Standard Error}
\note{Don't worry about the axes}
\note{Yes, the Implementation is better, we knew that, joins are
  naturally strong}
\note{``Union'', ``Optional'' and ``Lang'' demanding things}
\note{``BGPComp:Lang'' and ``Lang:Union'' interactions might be due to
  that many more triples need to be searched for a language tag in one
  of the levels of the interacting factors.}
\note{But what about ``Implement::TripleC''?}
\note{We want to do a hypothesis test}
\note{Two factors do not contribute significantly to the variation
  ``Range'' and ``Machine''}
